NIRCam Faint and Bright Flux Calibration Plan

### 2017-05-05 ms.tex
I put in a comparison of the spline fit rectification to piecewise polynomial.

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{colormag_two_runs.pdf}
\includegraphics[width=.49\columnwidth]{images/colormagNGC_2420_spline_rect.pdf}
\caption{\texttt{mkclass} is sensitive to the type of normalization I put into the rectified spectra. On the left, I used a piecewise 8th order polynomial. On the right side, I used a robust spline fit.
The spline fit reduces some of the crazy giants identified as G5 V, but also identifies some stars with near-solar colors as G8 V.}\label{fig:splineVsPiecewiseCM}
\end{figure}
